Data Management and Domain Adjusting Strategies for Implementing Parallel SPH Method in JPUE Simulation

### 2016-01-08 Paper for submission.tex
small modification

In both SPHysics\cite{dominguez2011optimization} and DualSPHysics\cite{crespo2015dualsphysics}, The physical quantities of each particle (position, velocity, density…) are stored in arrays, and the particles (and the arrays with particle data) are reordered following the order of the cells. This has two advantages: 1) access pattern is more regular and more efficient, 2) it is ease to identify the particles that belong to a cell by using a range since the first particle of each cell is known. But adding, deleting and especially accessing of particles are cumbersome. Ferrari\cite{ferrari2009new} adopted linked lists using pointers so that particles can be deleted or added during the simulation. Storage problems caused by fix-size arrays are thereby also eliminated. We define C++ classes which contains all data of particle and bucket. As for the management of data, we adopt hash tables to store pointers to particles and buckets, which give us not only flexibility of deleting and adding element, but also quicker access compared with linked list. Instead of using the "nature manner" to number particles, we adopt SFC based index to give each particle and background bucket an unique identifier -- a strategy known to preserve some locality at minimal cost. The SFC based numbering strategy is further extended to include time step information so that particles added at the same position but different time will have different identifiers. 

>>>>

In both SPHysics and DualSPHysics\cite{crespo2015dualsphysics}, the physical quantities of each particle (position, velocity, density…) are stored in arrays, and the particles (and the arrays with particle data) are reordered following the order of the cells. This has two advantages: 1) access pattern is more regular and more efficient, 2) it is ease to identify the particles that belong to a cell by using a range since the first particle of each cell is known. But adding, deleting and especially accessing of particles are cumbersome. Ferrari\cite{ferrari2009new} adopted linked lists using pointers so that particles can be deleted or added during the simulation. Storage problems caused by fix-size arrays are thereby also eliminated. We define C++ classes which contains all data of particle and bucket. As for the management of data, we adopt hash tables to store pointers to particles and buckets, which give us not only flexibility of deleting and adding element, but also quicker access compared with linked list. Instead of using the "nature manner" to number particles, we adopt SFC based index to give each particle and background bucket an unique identifier -- a strategy known to preserve some locality at minimal cost. The SFC based numbering strategy is further extended to include time step information so that particles added at the same position but different time will have different identifiers. 
